\chapter{Schedule of requirements}
\label{app:requirements}
\setheader{requirements}
This product consists of two parts: a function which gives the impulse response in different directions for a smartphone microphone and a measurement set-up description to add new data to this function.
This function will be part of a system which final objective is to enable crystal clear conference calls using an array of smartphones.
For this products, measurements to determine the impulse response for different directions are conducted on a commercially available smartphone.
These measurements need to be reproducible for any concerned smartphone, so manufacturers can add their own phones to the system, as input for the function.
The measurements and analyses carried out, are an extension of previous research 
\cite{Gaubitch2014}. 

The final product, the conference calling system, is intended for the professional market: large companies which make use of conference calling systems.
Next to that, smartphone manufacturers must be able to measure the impulse responses from their smartphones to apply this data to the function.

\section{Requirements concerning the intended use}
\begin{enumerate}
\item The function gives the impulse response for a given frequency and datapoint location.
\item The location of a datapoint is indicated by the angle between the projection of the vector pointing to this point on the $x,y$-plane and the $x$-axis ($\theta$) and the angle between the projection of this vector on the $x,z$-plane and the $z$-axis ($\phi$).
%\item The function must be usable by a user with little experience with \matlab. 
\item There must be an anechoic chamber available in order to do the measurements. 
\item The measurements concerning the directivity must be replicable within three days. 
\item The measurement results must be accurate enough to be used in a beamforming algorithm.  
\end{enumerate}

\section{Requirements from an ecological point of view}
There are no ecological requirements since the product solely consists of software. 

\section{Requirements concerning the system}

\subsection{Usage characteristics}
\begin{enumerate}
\item The function returns the impulse response for a given datapoint location.
\item The location of a datapoint is indicated by the angle between the projection of the vector pointing to this point on the $x,y$-plane and the $x$-axis ($\theta$) and the angle between the projection of this vector on the $x,z$-plane and the $z$-axis ($\phi$).
\item The function must be quick enough to be used in a beamforming algorithm. 
\item The function must have a clear overview provided with sufficient comments. 
\item The user must be able to retrieve results for not directly measured datapoints.
\item There must be a function which generates a spherical plot showing the entire three dimensional directivity gain pattern (in decibels) of the concerned smartphone microphone. 
\item The measurements could be done within three days. 
\end{enumerate}

\subsection{Production and commissioning characteristics}
\begin{enumerate}
\item The function must be usable by a user with {\matlab} Student R2014a.
\item The measurements must be replicable by a customer with an anechoic chamber available. 
\end{enumerate}

\subsection{Recycling features}
Recycling is not an issue since the product solely consists of software. 

\section{Requirements regarding the production}
\begin{enumerate}
\item {\matlab} must be available to run the measurement and directivity software. 
\item The function-code will be developed using {\matlab} Student R2014a. 
\item The measurement conducting system will be developed using {\matlab} Student R2014a. 
\item There must be an anechoic chamber available. 
\item There must be a turntable available (for example: Br\"uel \& Kj\ae r, system type 9640).
\item There must be a loudspeaker available.
\item There must be an arc with a 1-meter radius available.
\item There must be an audio interface available.
\end{enumerate}
% hierboven de benodigdheden nog aanpassen waarschijnlijk. 

\section{Requirements concerning the recycling system}
Recycling is not an issue since the product solely consists of software. 

\section{Requirements from a strategic, marketing and sales point of view}
\begin{enumerate}
\item The product must be directly available after purchase. 
\end{enumerate}